\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{microtype}
\usepackage{parskip}

\pagestyle{empty}

\begin{document}

\begin{flushright}
Tristan Farran\\
University of Amsterdam\\
\texttt{tristan.farran@student.uva.nl}\\[6pt]
\today
\end{flushright}

\bigskip

Dear Editors of the \textit{Electronic Journal of Statistics},

\bigskip

I am pleased to submit the manuscript \textbf{``When Your Model Stops Working: Anytime-Valid Calibration Monitoring''} for consideration for publication in the \textit{Electronic Journal of Statistics}.

\medskip
\textbf{Contributions.} The paper introduces PITMonitor, a sequential framework for detecting when a probabilistic forecaster loses calibration at deployment time. The core contribution is a family of e-processes built from Probability Integral Transform (PIT) residuals via plug-in martingales. These processes have three properties that, to my knowledge, are not simultaneously achieved
by existing approaches: (i)~they control the Type~I error at any stopping time without pre-specifying a sample size (anytime-validity); (ii)~they are distribution-free, requiring no parametric assumption on either the forecaster or the data stream; and (iii)~they admit an efficient $O(1)$ per-step update through a closed-form recursion, making them suitable for high-throughput deployment pipelines. The paper situates these contributions formally within the game-theoretic statistics literature (safe testing, e-values, e-detectors) and validates them empirically against seven baseline detectors across three structured drift scenarios.

\medskip
\textbf{Fit for EJS.} The \textit{Electronic Journal of Statistics} is the natural venue for this work. The paper's technical core is a theoretical result in sequential nonparametric testing - an area the journal has published extensively - and the motivating application (monitoring the calibration of deployed predictive models) is of broad statistical interest. The manuscript is self-contained, concise, and aimed squarely at a statistical methods audience.

\medskip
\textbf{Originality.} This manuscript is not under review at any other journal or conference, and the results have not been previously published.

\bigskip

Thank you for your time and consideration.

\bigskip

Sincerely,\\
Tristan Farran

\end{document}
